### 2024-03-11 sections/1stratified.tex
§1.3

\begin{example}
    Inspired by the previous example, any topological space $X$ with a filtration by closed subsets $\emptyset \subset X_{\leq 0} \subset \dots \subset X_{\leq n} = X$, is a stratified space, because the filtration induces a map $X \rightarrow \mathbb{N}$, which sends $X_{\leq i} \setminus X_{\leq i-1}$ to $i$.
\end{example}

@@

@@

A similar picture applies in the stratified case. As a first step, \cite[Corollary 2.13]{af_fhtop} shows that $M\mapsto\tau_M$ can be presented as the symmetric monoidal functor
%
\begin{equation}
    \tau: \mfld_n \xrightarrow{\mathrm{Yoneda}} \mathsf{PShv}(\mfld_n) \xrightarrow{-|_{\mathbb{R}^n \subset \mfld_n}} \mathsf{PShv}(\mathbb{R}^n) \simeq \mathsf{Spaces}_{/\mathsf{BO}(n)},
\end{equation}
where the codomain's symmetric monoidal structure is given by coproduct. As noted in \cite{af_fhtop}, the Kister--Mazur Theorem (\cite{kister1964microbundles}) provides an equivalence $\mathsf{Emb}(\mathbb{R}^n,\mathbb{R}^n)\simeq \mathsf{Top}(n)$, where $\mathsf{Top}(n)$ is the group of topological automorphisms of $\mathbb{R}^n$; $\mathsf{Emb}(\mathbb{R}^n,\mathbb{R}^n)\simeq\mfld_n(\mathbb{R}^n,\mathbb{R}^n)$ is the group of self-embeddings of $\mathbb{R}^n$; and both groups are equipped with the compact-open topology. This yields $\mathsf{PShv}(\mathbb{R}^n)\simeq\mathsf{PShv}(\mathsf{BTop}(n))$, which is equivalent to $\mathsf{Spaces}_{/\mathsf{BTop}(n)}$ by straightening-unstraightening (see \Cref{rem:grothendieck_construction}).\footnote{Presheaves are space-valued, that is, $\mathsf{PShv}(\mathscr{C})=\mathsf{Fun}(\mathscr{C}^{\mathsf{op}},\mathsf{Spaces})$.} Finally, the inclusion $\mathsf{O}(n)\hookrightarrow\mathsf{Emb}(\mathbb{R}^n,\mathbb{R}^n)$ is also an equivalence (\cite[Proposition 2.2.6]{af_primer}), yielding the displayed equivalence. The first map, the $\infty$-categorical Yoneda embedding, sends $M\mapsto((\mfld_{n})_{/M}\to\mfld_n)$ as a map with target $\mathsf{RFib}(\mfld_n)$, as in \cite{lurie_htt}. The fiber of $(\mfld_{n})_{/M}\to\mfld_n$ at $N$ is equivalent to the space of embeddings of $N$ into $M$, and so the restricted presheaf on the full sub-$\infty$-category at $\mathbb{R}^n$ sends $\mathbb{R}^n$ to the space of embeddings of $\mathbb{R}^n$ into $M$.

@@

\begin{remark}
    \Cref{thm:decom_strat_man} is the analogous theorem to handle decompositions of smooth manifolds. Namely, any compact, smooth manifold can be obtained by handle decomposition, and non-compact smooth manifolds are obtained by sequential colimits of finitary (including compact) smooth manifolds.
\end{remark}

@@

Along with the already familiar $\infty$-categories of basics $\mathsf{D}_n^{G} := \mathsf{B}G \xrightarrow{\{ \mathbb{R}^n\}} \bsc$, which govern smooth $n$-manifolds with $G$-structure, we introduce a few more $\infty$-categories of basics that will be useful for us. An $\infty$-category of basics that will play a big role for the development of factorization homology to come, is the particularly simple one describing oriented $1$-manifolds with boundary.

\begin{construction}\label{con:d_1^bor_structure}
    Consider the $\infty$-subcategory $\mathsf{D}_1^{\partial} \subset \bsc$ whose objects are $\mathbb{R}$ and $\hoint$. There is a unique right fibration $\mathsf{D}_1^{\partial, \mathsf{or}} \rightarrow \mathsf{D}_1^{\partial}$, whose fiber over $\mathbb{R}$ is a point $\{ \mathbb{R}\}$, and whose fiber over $\hoint$ is two points $\{ \hoint, {\mathbb{R}_{\leq 0}} \}$. In other words, $\mathsf{D}_1^{\partial, \mathsf{or}}$ has objects $\mathbb{R}$, $\hoint$ and $\mathbb{R}_{\leq 0}$ with their canonical orientations, and the morphisms are orientation preserving embeddings between them. In this way, $\mathsf{D}_1^{\partial, \mathsf{or}}$ is the $\infty$-category of basics that describes oriented (or, equivalently in this case, framed), smooth 1-manifolds with boundary.
\end{construction}

@@

\begin{construction}[{\cite[ex.5.2.10]{aft_localstrut}}]
    Let $\mathsf{D}_{d \subset n} \subset \bsc$ be the full $\infty$-subcategory whose objects are $\mathbb{R}^n$ and $\mathbb{R}^{d \subset n} := \mathbb{R}^{n-d} \times \mathsf{C}(S^{n-d-1})$, where $d < n$. We elaborate that the morphism spaces are given as follows:
    %
    \begin{enumerate}
        \item $\mathsf{Hom}_{\mathsf{D}_{d \subset n}} (\mathbb{R}^n, \mathbb{R}^n) = \mathsf{Emb}(\mathbb{R}^n, \mathbb{R}^n)$, the space of smooth embeddings of $\mathbb{R}^n$.
        \item $\mathsf{Hom}_{\mathsf{D}_{d \subset n}} (\mathbb{R}^{d \subset n}, \mathbb{R}^n) = \emptyset$
        \item $\mathsf{Hom}_{\mathsf{D}_{d \subset n}} (\mathbb{R}^n, \mathbb{R}^{d \subset n}) = \mathsf{Emb}(\mathbb{R}^n, \mathbb{R}^n \setminus \mathbb{R}^d)$, the space of embeddings that miss the defect.
        \item $\mathsf{Hom}_{\mathsf{D}_{d \subset n}} (\mathbb{R}^{d \subset n}, \mathbb{R}^{d \subset n}) \simeq \mathsf{O}(d) \times \mathsf{O}(n-d)$. This final morphism space is given differently compared to the other ones because of intricacies related to smoothness around the defect. For more details on the matter there is a discussion in \cite[ex.5.1.7]{aft_localstrut}.
    \end{enumerate}
    %
    That $\mathsf{D}_{d \subset n} \rightarrow \bsc$ is a right fibration is immediate from the fact that the objects of $\mathsf{D}_{d \subset n}$ have at most one defect, which means that they don't receive maps from basics that are not in $\mathsf{D}_{d \subset n}$ already.
\end{construction}

@@

    Explaining what exactly we mean by a framed stratified manifold is done in \cite[ex.5.2.12]{aft_localstrut}. According to that example, $\mathsf{D}_{d \subset n}^*$-manifolds are described by the data of a framed smooth $n$-manifold $M$, a properly embedded smooth $d$-submanifold $\Sigma$ together with a null-homotopy of the Gauss map $\Sigma \rightarrow \mathsf{Gr}_d(\mathbb{R}^n)$. In more detail, for a general embedded submanifold $\Sigma \xhookrightarrow{} M$ the Gauss map gives the tangent (or equivalently normal) subspace to $\Sigma$ at every point. That is encoded as a map $\Sigma \rightarrow \mathsf{Gr}_d(\mathsf{T}M)$ to the Grassmann bundle of the tangent bundle of $M$. In our case, the framing of $M$ provides a preferred trivialization of the tangent bundle to $\mathbb{R}^n$. A null-homotopy of this map is a trivialization of the tangent (and subsequently also the normal) bundle of $\Sigma$ in a way that is compatible with the trivialization of $\mathsf{T}M$.
\end{remark}

>>>>

\begin{example}\label{7UEDP24}
    Inspired by the previous example, any topological space $X$ with a filtration by closed subsets $\emptyset \subset X_{\leq 0} \subset \dots \subset X_{\leq n} = X$, is a stratified space, because the filtration induces a map $X \rightarrow \mathbb{N}$, which sends $X_{\leq i} \setminus X_{\leq i-1}$ to $i$.
\end{example}

@@

\begin{example}
    The open cone $C(S^k)$ on the $k$-sphere is canonically identified with $\mathbb{R}^k$ with stratification given by the filtration $\{0\}\subset\mathbb{R}^k$ as in \Cref{7UEDP24}.
\end{example}

@@

A similar picture applies in the stratified case. As a first step, \cite[Corollary 2.13]{af_fhtop} shows that $M\mapsto\tau_M$ can be presented as the symmetric monoidal functor
%
\begin{equation}
    \tau: \mfld_n \xrightarrow{\mathrm{Yoneda}} \mathsf{PShv}(\mfld_n) \xrightarrow{-|_{\mathbb{R}^n \subset \mfld_n}} \mathsf{PShv}(\mathbb{R}^n) \simeq \mathsf{Spaces}_{/\mathsf{BO}(n)},
\end{equation}
where the codomain's symmetric monoidal structure is given by coproduct.

\begin{remark}\label{9EFM44H}
    As noted in \cite{af_fhtop}, the Kister--Mazur Theorem (\cite{kister1964microbundles}) provides an equivalence $\mathsf{Emb}(\mathbb{R}^n,\mathbb{R}^n)\simeq \mathsf{Top}(n)$, where $\mathsf{Top}(n)$ is the group of topological automorphisms of $\mathbb{R}^n$; $\mathsf{Emb}(\mathbb{R}^n,\mathbb{R}^n)\simeq\mfld_n(\mathbb{R}^n,\mathbb{R}^n)$ is the group of self-embeddings of $\mathbb{R}^n$; and both groups are equipped with the compact-open topology. This yields $\mathsf{PShv}(\mathbb{R}^n)\simeq\mathsf{PShv}(\mathsf{BTop}(n))$, which is equivalent to $\mathsf{Spaces}_{/\mathsf{BTop}(n)}$ by straightening-unstraightening (see \Cref{rem:grothendieck_construction}).\footnote{Presheaves are space-valued, that is, $\mathsf{PShv}(\mathscr{C})=\mathsf{Fun}(\mathscr{C}^{\mathsf{op}},\mathsf{Spaces})$.} Finally, the inclusion $\mathsf{O}(n)\hookrightarrow\mathsf{Emb}(\mathbb{R}^n,\mathbb{R}^n)$ is also an equivalence (\cite[Proposition 2.2.6]{af_primer}), yielding the displayed equivalence. The first map, the $\infty$-categorical Yoneda embedding, sends $M\mapsto((\mfld_{n})_{/M}\to\mfld_n)$ as a map with target $\mathsf{RFib}(\mfld_n)$, as in \cite{lurie_htt}. The fiber of $(\mfld_{n})_{/M}\to\mfld_n$ at $N$ is equivalent to the space of embeddings of $N$ into $M$, and so the restricted presheaf on the full sub-$\infty$-category at $\mathbb{R}^n$ sends $\mathbb{R}^n$ to the space of embeddings of $\mathbb{R}^n$ into $M$. 
\end{remark}

@@

\begin{remark}
    \Cref{thm:decom_strat_man} is the analogue of handle decompositions for smooth manifolds. Namely, any compact, smooth manifold can be obtained by handle decomposition, and non-compact smooth manifolds are obtained by sequential colimits of finitary (including compact) smooth manifolds.
\end{remark}

@@

Along with the already familiar $\infty$-categories of basics $\mathsf{D}_n^{G} := \mathsf{B}G \xrightarrow{\{ \mathbb{R}^n\}} \bsc$, which govern smooth $n$-manifolds with $G$-structure, we recall a few more $\infty$-categories of basics that will be of interest to us.

\begin{example}[{\cite[Example 5.2.5]{aft_localstrut}}]
    We denote by $\mathsf{D}_n\hookrightarrow \bsc$ or simply $\mathsf{D}_n$ the tangential structure given by the full sub-$\infty$-category inclusion of $\bsc_{0,n}$, the basics of depth $0$ and pure dimension $n$.\footnote{A stratified space $X\to P$ has \emph{pure dimension $n$} (\cite[Definition 2.4.1]{aft_localstrut}) if its local (\v{C}ech--Lebesgue) dimension $\mathsf{dim}_x(X)$ at every $x\in X$ is $n$. Connected topological manifolds are of this type.} Accordingly, $\mathsf{D}_n$-manifolds are topological $n$-manifolds. As in \Cref{9EFM44H}, we have an equivalence $\mathsf{D}_n\simeq \mathsf{BGL}(n)\simeq \mathsf{BO}(n)$ of $\infty$-groupoids.
\end{example}

An $\infty$-category of basics that will play a major role for the development of factorization homology to come is the particularly simple one describing oriented $1$-manifolds with boundary.

\begin{construction}\label{con:d_1^bor_structure}
    Consider the $\infty$-subcategory $\mathsf{D}_1^{\partial} \subset \bsc$ whose objects are $\mathbb{R}$ and $\hoint=C(\ast)$. There is a unique right fibration $\mathsf{D}_1^{\partial, \mathsf{or}} \rightarrow \mathsf{D}_1^{\partial}$, whose fiber over $\mathbb{R}$ is a point $\{ \mathbb{R}\}$, and whose fiber over $\hoint$ is two points $\{ \hoint, {\mathbb{R}_{\leq 0}} \}$. In other words, $\mathsf{D}_1^{\partial, \mathsf{or}}$ has objects $\mathbb{R}$, $\hoint$ and $\mathbb{R}_{\leq 0}$ with their canonical orientations, and the morphisms are orientation preserving embeddings between them. In this way, $\mathsf{D}_1^{\partial, \mathsf{or}}$ is the $\infty$-category of basics that describes oriented (or, equivalently in this case, framed), smooth 1-manifolds with boundary.
\end{construction}

\begin{remark}
    Insisting that tangential structures be \emph{right fibrations} over $\bsc$, as opposed to simply $\infty$-categories over it as, e.g., in \cite{ayala2020factorization}, leads to technical issues that lead to our over-simplified notation due to the property of being a right fibration not being invariant under equivalence. For instance, when $G=\ast$, so that $\mathsf{D}^\ast_n$ constrols framed $n$-manifolds, the map $BG=\ast\to \mathsf{BO}(n)\simeq\mathsf{D}_n$ is not a right fibration, owing to the observation that right fibrations of Kan complexes are Kan fibrations, and these, when surjective on objects, are epimorphisms. On the other hand, $B\ast=\ast\simeq (\mathsf{D}_n)_{/\mathbb{R}^n}$ since over-$\infty$-groupoids are contractible (\cite[018Y]{lurie_kerodon}), but $(\mathsf{D}_n)_{/\mathbb{R}^n}\to \mathsf{D}_n$ \emph{is} a right fibration since it is a projection from an over-$\infty$-category (\cite[Proposition 018F]{lurie_kerodon}, \cite{joyal}). Moreover, $\mathsf{D}_n\hookrightarrow \bsc$ is a right fibration since this full sub-$\infty$-category is trivially a sieve, so the composition $(\mathsf{D}_n)_{/\mathbb{R}^n}\to \bsc$ is a right fibration as well. In general, the map $\mathsf{B}G\to \mathsf{BO}(n)$ is not a right fibration unless $G\to\mathsf{O}(n)$ is an epimorphism. However, given the latter, we can consider the presheaf $\mathsf{D}_n^{\text{op}}\to\mathsf{Spaces}$ given by mapping $\mathbb{R}^n$ to the space of $G$-structures on it, and sending an embedding to the induced pullback map on the respective spaces of $G$-structures. By unstraightening, this determines a right fibration for which, by abuse, we write $\mathsf{D}^G_n=\mathsf{B}G\to \mathsf{D}_n\hookrightarrow\bsc$.
\end{remark}

@@

\begin{construction}[{\cite[Example 5.2.10]{aft_localstrut}}]
    Let $\mathsf{D}_{d \subset n} \subset \bsc$ be the full $\infty$-subcategory whose objects are $\mathbb{R}^n$ and $\mathbb{R}^{d \subset n} := \mathbb{R}^{d} \times \mathsf{C}(S^{n-d-1})$, where $d < n$. We elaborate that the morphism spaces are given as follows:
    %
    \begin{enumerate}
        \item $\mathsf{Hom}_{\mathsf{D}_{d \subset n}} (\mathbb{R}^n, \mathbb{R}^n) = \mathsf{Emb}(\mathbb{R}^n, \mathbb{R}^n)$, the space of smooth embeddings of $\mathbb{R}^n$.
        \item $\mathsf{Hom}_{\mathsf{D}_{d \subset n}} (\mathbb{R}^{d \subset n}, \mathbb{R}^n) = \emptyset$
        \item $\mathsf{Hom}_{\mathsf{D}_{d \subset n}} (\mathbb{R}^n, \mathbb{R}^{d \subset n}) = \mathsf{Emb}(\mathbb{R}^n, \mathbb{R}^n \setminus \mathbb{R}^d)$, the space of embeddings that miss the defect.
        \item $\mathsf{Hom}_{\mathsf{D}_{d \subset n}} (\mathbb{R}^{d \subset n}, \mathbb{R}^{d \subset n}) \simeq \mathsf{O}(d) \times \mathsf{O}(n-d)$. This final morphism space is given differently compared to the other ones because of intricacies related to smoothness around the defect. For more details on the matter there is a discussion in \cite[Example 5.1.7]{aft_localstrut}.
    \end{enumerate}
    %
    That $\mathsf{D}_{d \subset n} \rightarrow \bsc$ is a right fibration is immediate from the fact that the objects of $\mathsf{D}_{d \subset n}$ have at most one defect, which means that they don't receive maps from basics that are not in $\mathsf{D}_{d \subset n}$ already.
\end{construction}

@@

    Explaining what exactly we mean by a framed stratified manifold is done in \cite[Example 5.2.12]{aft_localstrut}. According to that example, $\mathsf{D}_{d \subset n}^*$-manifolds are described by the data of a framed smooth $n$-manifold $M$, a properly embedded smooth $d$-submanifold $\Sigma$ together with a null-homotopy of the Gauss map $\Sigma \rightarrow \mathsf{Gr}_d(\mathbb{R}^n)$. In more detail, for a general embedded submanifold $\Sigma \xhookrightarrow{} M$ the Gauss map gives the tangent (or equivalently normal) subspace to $\Sigma$ at every point. That is encoded as a map $\Sigma \rightarrow \mathsf{Gr}_d(\mathsf{T}M)$ to the Grassmann bundle of the tangent bundle of $M$. The framing of $M$ is a diffeomorphism of type $\mathsf{T}M\cong M\times\mathbb{R}^n$ over, reducing said map to the Gauss map. A null-homotopy of this map is a trivialization of the tangent as well as the normal bundles of $\Sigma$ in a way that is compatible with the trivialization of the restriction of $\mathsf{T}M$ to $\Sigma$.
\end{remark}
